High Contrast Coronagraphy

### 2025-01-09 src/tex/ms.tex
fixed Maxwell

\begin{table}
\caption{Definition of physical quantities}\label{tab1}
\begin{center}
\begin{tabular}{@{}l|l|l|l@{}}
\hline
$i$ & The imaginary unit & $c$ & Speed of light in a vacuum \\\hline
$\vec{E}$ & Electric field & $\vec{H}$ & Magnetic field \\\hline
$\mathcal{D}$ & Displacement field & $\mathcal{B}$ & Magnetizing field \\\hline
$\epsilon$ & Electric permittivity & $\epsilon_0$ & Electric permittivity of vacuum \\\hline
$\mu$ & Magnetic permittivity & $\mu_0$ & Magnetic permittivity of vacuum \\\hline
$\omega$ & Wavenumber & $\vec{k}$ & Wavevector \\\hline
$\lambda$ & Wavelength & $\lambda_0$ & Center wavelength in the bandpass \\\hline
$\Pi$ & The telescope pupil function & $\Delta\lambda$ & The width of the bandpass \\\hline
$D$ & Diameter of the pupil & $n$ & (Complex) refractive index of macroscopic media \\\hline
$\mathcal{F}_{x,y}[\cdot]$ & Fourier transform operator & $\mathcal{F}^{-1}_{x,y}[\cdot]$ & Inverse Fourier transform operator \\\hline
$C_\lambda[\cdot]$ & A general coronagraph propagation operator & $\Psi_\lambda[\vec{k}]$ & Coronagraphic image \\\hline
$\phi$ & The phase of the electric field & $\alpha$ & The amplitude of the electric field \\\hline
\hline
\end{tabular}
\end{center}
\end{table}

The vast majority of energy from astrophysical objects arrives at our telescopes in the form of electromagnetic radiation.
%
This time-dependent interaction is described by Maxwell's equations (with relevant physical quantities defined in Table \ref{tab1}),

@@

This form of Maxwell's equations is in the material form without any charge and current sources.
%
The material form is used to describe the propagation of electromagnetic fields inside matter.
%
This set of equations is completed by describing the particular matter of the medium with the constitutive relations, $\mathcal{D}=\epsilon \mathcal{E}$ and $\mathcal{B}=\mu \mathcal{H}$. 
%
Here $\epsilon$ and $\mu$ are the permittivity and magnetic permeability, respectively.
%
The wave equation for electromagnetic waves can be derived by taking the curl of Ampere's law.
%
This gives us the classic wave equation if we assume that the EM wave propagates in isotropic and homogeneous materials,
\begin{equation}
\label{eq:wave_eq}
\begin{aligned}
\mu \epsilon \frac{\partial^2 \mathcal{E}}{\partial t^2} - \nabla^2\mathcal{E} = 0 .
\end{aligned}
\end{equation}
We consider a purely monochromatic EM wave with frequency $\omega$.
%
The wave function is then $\mathcal{E}=\psi(r) e^{iwt}$ with $\psi(r)$ describing the spatial distribution.
%
Substituting this relation into Equation \ref{eq:wave_eq},
\begin{equation}
\nabla^2\mathcal{E} +\mu \epsilon \omega^2 \mathcal{E} = 0.
\end{equation}
The usual definition of the permittivity and permeability are $\epsilon=\epsilon_r \epsilon_0$ and $\mu=\mu_r \mu_0$ with $\epsilon_r$ and $\mu_r$ the relative permittivity and permeability compared to that of vacuum, $\epsilon_0$ and $\mu_0$.
%
In optics most glasses and materials are defined by their refractive index $n$ which is related to permittivity as $\epsilon_r = n^2$ and many of these are also non-magnetic which means that $\mu_r=1$.
%
Substituting this will give us the classic Helmholtz equation
\begin{equation}
\nabla^2\mathcal{E} + n^2k^2 \mathcal{E} = 0,
\end{equation}
We made use of the fact that the speed of light is $c = \frac{1}{\sqrt{\epsilon_0\mu_0}}$ and that $k = c\omega$ is the wave number.
%
The propagation through an optical system has a preferential direction that is usually defined along the z-axis.
%
The z-axis evolution can be derived by separating the spatial components into the z component and the perpendicular components (x,y),
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -\nabla_{\perp}^2\mathcal{E}-n^2k^2 \mathcal{E},
\end{equation}
This differential equation can be solved by assuming a plane wave expansion $\mathcal{E}(x,y,z)=e^{i(k_x x + k_y y)}f(z)$ which results in
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -(n^2k^2 - k_{\perp}^2)\mathcal{E}.
\end{equation}
The solution to this equation is the so called Angular Spectrum Propagator that relates the electric field at any one plane to the electric field at any other,
\begin{equation}
\label{eq:angular_spectrum}
\mathcal{E}(x, y, z') = \mathcal{F}_{x,y}^{-1}\{e^{-ik_z(z'-z)}\mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}

Here the $z$ component of the wave vector is defined as $k_z=\sqrt{n^2k^2 - k_{\perp}^2}$ and $\mathcal{F}_{x,y}^{(-1)}$ is defined as the (inverse) Fourier transform over the x and y coordinates.
%
While Equation \ref{eq:angular_spectrum} describes the full propagation from one plane to another, it is quite unwieldy to use and does not provide much physical insight.
%
For many optical systems it is sufficient to analyze the paraxial performance.
%
The paraxial approximation assumes that the plane waves make small angles with respect to the z-axis which means that the $x$ and $y$ wave vector components are $k_x,k_y<<1$.
%
In this regime the propagation factor $k_z=\sqrt{n^2k^2 - k_{\perp}^2}\approx nk - \frac{k_{\perp}^2}{2nk}$ and the Fresnel propagation equation becomes
\begin{equation}
\label{eq:angular_spectrum2}
\mathcal{E}(x, y, z') = e^{-ink(z'-z)} \mathcal{F}_{x,y}^{-1}\{ e^{-i\frac{k_{\perp}^2}{2nk}} \mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}
The real space solution that is derived from the propagation equation is the classical Fresnel diffraction equation,
\begin{equation}
\label{eq:fresnel_diffraction}
\mathcal{E}(x, y, z') = \frac{e^{-ink(z'-z)}}{\lambda z} \iint_{-\infty}^{\infty} \mathcal{E}(u, v, z) e^{\frac{ik\left[(x - u)^2 + (y - v)^2\right]}{2 (z' - z)}} \mathrm{d}u \mathrm{d}v.
\end{equation}
The far-field approximation ($z \gg x, y$) and the substitution $\theta_x = \frac{x}{\lambda z}$, $\theta_y = \frac{y}{\lambda z}$ results in the Fraunhofer diffraction integral,
\begin{equation}
\label{eq:fraunhofer_diffraction}
\mathcal{E}(\theta_x, 
\theta_y) \propto \iint_{-\infty}^{\infty} \mathcal{E}(u, v) e^{-i2\pi(\theta_x u + \theta_y v)} \mathrm{d}u \mathrm{d}v.
\end{equation}
This shows that the far-field distribution of an electromagnetic wave is it's Fourier transform. A perfectly aligned lens, or the mirrors of a telescope, brings rays that come from infinity to the focal point. This is identical to a far-field transform, and therefore the operation of a lens can be described by the Fraunhofer diffraction integral.

@@

The fundamental goal of any coronagraph is to block the light from the star, while passing through the light of the planet.
%
Any type of \ac{fpm} coronagraph, like the Classic Lyot coronagraph, will find that it is very difficult to completely null out the star.
%
This is due to a mismatch between the modes of the incoming electric field from the aperture and the \ac{fpm} filtered electric field.
%
The propagation through a Classic Lyot style coronagraph can be described by two propagations.
%
The first is a propagation through the area that is covered by the mask itself, $m_1$, and the second is the negative of the mask $m_2$.
%
Together, these two masks cover the full focal plane.
%
The propagation of the electric fields then follow as,
\begin{equation}
    E_{\mathrm{out}} = t\invfourier{m_1 \fourier{E_{in}}} + \invfourier{m_2 \fourier{E_{in}}}.
\end{equation}
Now let's simplify this by substituting $\hat{m}=\fourier{m_1}$, $m_2 = 1 - m_1$ and using the Fourier convolution theorem. This results in a simplified equation,
\begin{equation}
    E_{\mathrm{out}} = E_{in} + (t-1)\hat{m}*E_{in}.
\end{equation}
The output is the sum of two electric fields, the original input electric field and a filtered electric field.
%
The filtered light is allowed to diffract light outside the geometric pupil because this is blocked by the Lyot stop.
%
Therefore, the condition for perfect nulling is found by setting the output over the geometric pupil to zero. 
\begin{equation}
    E_{in} + (t-1)\hat{m}*E_{in} = 0.
\end{equation}
This condition can only be fulfilled if the incoming electric field is an eigenfunction of the filtering operator.
\begin{equation}
    \hat{m}*E_{in} = \gamma E_{in}.
\end{equation}
Then
\begin{equation}
    E_{in} + (t-1)\gamma E_{in} = 0,
\end{equation}
and a perfect null is achieved when $(t-1)\gamma = -1$.
%
The normal pupil illumination is uniform and is not an eigenfunction of the filtering operator.
%
Therefore, it is not possible to perfectly null the starlight with any type of Lyot-style \ac{fpm}.
%
These eigenfunctions are Prolate Spheroids and they generate theoretically perfect nulls if combined with the Roddier \& Roddier coronagraphs \citep{soummer2003stellar}.

@@

\begin{equation}
    \hat{v} = \argmin_v \int_S |E_{s}(x,y) + E_{\mathrm{DM}}(x, y, v)|^2\mathrm{d}A.
\end{equation}

Here $v$ is the \ac{dm} command, $E_{s}$ the stellar speckles in the coronagraphic focal plane and $E_{\mathrm{DM}}$ the speckles created by the \ac{dm}.
%
Effectively, \ac{efc} finds the command that injects speckles with the exact same amplitude but opposite phase in the focal plane.
%
\ac{efc} is currently the most used and best optimized algorithm on testbeds and instruments \citep{Mennesson24}.

@@

Estimating the stellar halo with images at nearby wavelengths was generalised with the use of integral field spectrographs, where many science camera \acp{psf} are sampled at different wavelengths simultaneously to form $(x,y,\lambda)$ data cubes.
%
Resampling the image slices into the same \ld{} spatial scale radially smears out any exoplanet signal, so subtracting off a median of these images removes the stellar halo but keeps most of the planet flux intact, making it visible when the median subtracted cube is resampled into the sky coordinates and combined to produce the \ac{psf} subtracted image, generalised as Spectral Differential Imaging \cite[SDI; ][]{Sparks02} and demonstrated on-sky with SINFONI \citep{Thatte07}.

For higher spectral resolutions, the spectrum of the exoplanet begins to resolve the individual rotational-vibrational transitions, enabling High Spectral Contrast Imaging \citep[including the detection of HD~209458b ][]{Snellen10} and then generalising into the principle of molecule mapping in directly imaged exoplanets such as Beta~Pictoris~b \citep{Hoeijmakers18}.

Stochastic Speckle Discriminaton \citep[SSD; ][]{Gladysz09} is possible using short exposure images with the Airy core unsaturated.
%
Photon counting devices enable this detection method to work - this was demonstrated using an MKID detector and has led to the discovery of a substellar companion using this technique \citep{Steiger21}.

Each diversity improves sensitivity from a factor of a few to ten or more.
%
Combining different diversities together results in an even greater cumulative effect.

@@

To achieve the scientific results presented in this article we made use of the \emph{Python} programming language\footnote{Python Software Foundation, \url{https://www.python.org/}}, especially the \emph{SciPy} \citep{virtanen2020}, \emph{NumPy} \citep{numpy}, \emph{Matplotlib} \citep{Matplotlib}, \emph{emcee} \citep{foreman-mackey2013}, and \emph{astropy} \citep{astropy_1,astropy_2} packages.
%
The \ac{hci} simulations were calculated with \emph{HCIpy} \citep{Por18}.
%
This Article is reproducible using the \emph{showyourwork!} workflow management tool \citep{Luger2021}.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
M.\ A.\ K.\ acknowledges useful conversations with several people (most notably
Phil Hinz, Andrew Skemer and Eric Mamajek) at the Humble Sea Brewing Company.

>>>>

\begin{table}
\caption{Definition of physical quantities}\label{tab1}
\begin{center}
\begin{tabular}{@{}l|l|l|l@{}}
\hline
$i$ & The imaginary unit & $c$ & Speed of light in a vacuum \\\hline
$\mathcal{E}$ & Electric field & $\mathcal{H}$ & Magnetic field \\\hline
$\mathcal{D}$ & Electric displacement & $\mathcal{B}$ & Magnetic induction \\\hline
$\epsilon$ & Relative electric permittivity & $\epsilon_0$ & Electric permittivity of vacuum \\\hline
$\mu$ & Relative magnetic permeability & $\mu_0$ & Magnetic permeability of vacuum \\\hline
$\omega$ & Angular frequency & $|\vec{k}|$ & Wave number \\\hline
$\lambda$ & Wavelength & $\lambda_0$ & Central wavelength in the bandpass \\\hline
$\Pi$ & The telescope pupil function & $\Delta\lambda$ & The width of the bandpass \\\hline
$D$ & Diameter of the pupil & $n$ & (Complex) refractive index of macroscopic media \\\hline
$\mathcal{F}_{x,y}[\cdot]$ & Fourier transform operator & $\mathcal{F}^{-1}_{x,y}[\cdot]$ & Inverse Fourier transform operator \\\hline
$C_\lambda[\cdot]$ & A general coronagraph propagation operator & $\Psi_\lambda[\vec{k}]$ & Coronagraphic image \\\hline
$\phi$ & The phase of the electric field & $\alpha$ & The amplitude of the electric field \\\hline
\hline
\end{tabular}
\end{center}
\end{table}

The vast majority of energy from astrophysical objects arrives at our telescopes in the form of electromagnetic radiation.
%
This time-dependent interaction is described by Maxwell's equations \citep[with relevant physical quantities defined in Table \ref{tab1} and following ][]{Lavrinenko14},

@@

This form of Maxwell's equations is in the material form without any charge and current sources.
%
The material form is used to describe the propagation of electromagnetic fields inside matter.
%
This set of equations is completed by describing the particular matter of the medium with the constitutive relations, $\mathcal{D}=\epsilon \mathcal{E}$ and $\mathcal{B}=\mu \mathcal{H}$. 
%
Here $\epsilon$ and $\mu$ are the permittivity and magnetic permeability, respectively.
%
The wave equation for electromagnetic waves can be derived by taking the curl of Ampere's law.
%
This gives us the classic wave equation if we assume that the EM wave propagates in isotropic and homogeneous materials,
\begin{equation}
\label{eq:wave_eq}
\begin{aligned}
\mu \epsilon\frac{\partial^2 \mathcal{E}}{\partial t^2} - \nabla^2\mathcal{E} = 0 .
\end{aligned}
\end{equation}
We consider a purely monochromatic EM wave with angular frequency $\omega$.
%
The wave function is then $\mathcal{E}=\psi(r) e^{iwt}$ with $\psi(r)$ describing the spatial distribution.
%
Substituting this relation into Equation \ref{eq:wave_eq},
\begin{equation}
\nabla^2\mathcal{E} +\mu \epsilon \omega^2 \mathcal{E} = 0.
\end{equation}
The usual definition of the permittivity and permeability are $\epsilon=\epsilon_r \epsilon_0$ and $\mu=\mu_r \mu_0$ with $\epsilon_r$ and $\mu_r$ the relative permittivity and permeability compared to that of vacuum, $\epsilon_0$ and $\mu_0$.
%
In optics most glasses and materials are defined by their refractive index $n$ which is related to permittivity as $\epsilon_r = n^2$ and many of these are also non-magnetic which means that $\mu_r=1$.
%
Substituting this will give us the classic Helmholtz equation
\begin{equation}
\nabla^2\mathcal{E} + n^2k^2 \mathcal{E} = 0,
\end{equation}
We made use of the fact that the speed of light is $c = \frac{1}{\sqrt{\epsilon_0\mu_0}}$ and that $k = c\omega$ is the wave number.
%
The propagation through an optical system has a preferential direction that is usually defined along the z-axis.
%
The z-axis evolution can be derived by separating the spatial components into the z component and the perpendicular components (x,y),
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -\nabla_{\perp}^2\mathcal{E}-n^2k^2 \mathcal{E},
\end{equation}
This differential equation can be solved by assuming a plane wave expansion $\mathcal{E}(x,y,z)=e^{i(k_x x + k_y y)}f(z)$ which results in
\begin{equation}
\frac{\partial^2\mathcal{E}}{\partial z^2} = -(n^2k^2 - k_{\perp}^2)\mathcal{E}.
\end{equation}
The solution to this equation is the so called Angular Spectrum Propagator that relates the electric field at any one plane to the electric field at any other,
\begin{equation}
\label{eq:angular_spectrum}
\mathcal{E}(x, y, z') = \mathcal{F}_{x,y}^{-1}\{e^{-ik_z(z'-z)}\mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}

Here the $z$ component of the wave vector is defined as $k_z=\sqrt{n^2k^2 - k_{\perp}^2}$ and $\mathcal{F}_{x,y}^{(-1)}$ is defined as the (inverse) Fourier transform over the x and y coordinates.
%
While Equation \ref{eq:angular_spectrum} describes the full propagation from one plane to another, it is quite unwieldy to use and does not provide much physical insight.
%
For many optical systems it is sufficient to analyze the paraxial performance.
%
The paraxial approximation assumes that the plane waves make small angles with respect to the z-axis which means that the $x$ and $y$ wave vector components are $k_x,k_y<<1$.
%
In this regime the propagation factor $k_z=\sqrt{n^2k^2 - k_{\perp}^2}\approx nk - \frac{k_{\perp}^2}{2nk}$ and the Fresnel propagation equation becomes
\begin{equation}
\label{eq:angular_spectrum2}
\mathcal{E}(x, y, z') = e^{-ink(z'-z)} \mathcal{F}_{x,y}^{-1}\{ e^{-i\frac{k_{\perp}^2}{2nk}} \mathcal{F}_{x,y}\{\mathcal{E}(x,y,z)\}\}.
\end{equation}
The real space solution that is derived from the propagation equation is the classical Fresnel diffraction equation,
\begin{equation}
\label{eq:fresnel_diffraction}
\mathcal{E}(x, y, z') = \frac{e^{-ink(z'-z)}}{\lambda z} \iint_{-\infty}^{\infty} \mathcal{E}(u, v, z) e^{\frac{ik\left[(x - u)^2 + (y - v)^2\right]}{2 (z' - z)}} \mathrm{d}u \mathrm{d}v.
\end{equation}
The far-field approximation ($z \gg x, y$) and the substitution $\theta_x = \frac{x}{\lambda z}$, $\theta_y = \frac{y}{\lambda z}$ results in the Fraunhofer diffraction integral,
\begin{equation}
\label{eq:fraunhofer_diffraction}
\mathcal{E}(\theta_x, 
\theta_y) \propto \iint_{-\infty}^{\infty} \mathcal{E}(u, v) e^{-i2\pi(\theta_x u + \theta_y v)} \mathrm{d}u \mathrm{d}v.
\end{equation}
This shows that the far-field distribution of an electromagnetic wave is its Fourier transform.
%
A perfectly aligned lens, or the mirrors of a telescope, brings rays that come from infinity to the focal point.
%
This is identical to a far-field transform, and therefore the operation of a lens can be described by the Fraunhofer diffraction integral.

@@

The fundamental goal of any coronagraph is to block the light from the star, while passing through the light of the planet.
%
Any type of \ac{fpm} coronagraph, like the Classic Lyot coronagraph, will find that it is very difficult to completely null out the star.
%
This is due to a mismatch between the modes of the incoming electric field from the aperture and the \ac{fpm} filtered electric field.
%
The propagation through a Classic Lyot style coronagraph can be described by two propagations.
%
The first is a propagation through the area that is covered by the mask itself, $m_1$, and the second is the negative of the mask $m_2$.
%
Together, these two masks cover the full focal plane.
%
The propagation of the electric fields then follow as,
\begin{equation}
    \mathcal{E}_{\mathrm{out}} = t\invfourier{m_1 \fourier{\mathcal{E}_{in}}} + \invfourier{m_2 \fourier{\mathcal{E}_{in}}}.
\end{equation}
Now let's simplify this by substituting $\hat{m}=\fourier{m_1}$, $m_2 = 1 - m_1$ and using the Fourier convolution theorem. This results in a simplified equation,
\begin{equation}
    \mathcal{E}_{\mathrm{out}} = \mathcal{E}_{in} + (t-1)\hat{m}*\mathcal{E}_{in}.
\end{equation}
The output is the sum of two electric fields, the original input electric field and a filtered electric field.
%
The filtered light is allowed to diffract light outside the geometric pupil because this is blocked by the Lyot stop.
%
Therefore, the condition for perfect nulling is found by setting the output over the geometric pupil to zero. 
\begin{equation}
    \mathcal{E}_{in} + (t-1)\hat{m}*\mathcal{E}_{in} = 0.
\end{equation}
This condition can only be fulfilled if the incoming electric field is an eigenfunction of the filtering operator.
\begin{equation}
    \hat{m}*\mathcal{E}_{in} = \gamma \mathcal{E}_{in}.
\end{equation}
Then
\begin{equation}
    \mathcal{E}_{in} + (t-1)\gamma \mathcal{E}_{in} = 0,
\end{equation}
and a perfect null is achieved when $(t-1)\gamma = -1$.
%
The normal pupil illumination is uniform and is not an eigenfunction of the filtering operator.
%
Therefore, it is not possible to perfectly null the starlight with any type of Lyot-style \ac{fpm}.
%
These eigenfunctions are Prolate Spheroids and they generate theoretically perfect nulls if combined with the Roddier \& Roddier coronagraphs \citep{soummer2003stellar}.

@@

\begin{equation}
    \hat{v} = \argmin_v \int_S |\mathcal{E}_{s}(x,y) + \mathcal{E}_{\mathrm{DM}}(x, y, v)|^2\mathrm{d}A.
\end{equation}

Here $v$ is the \ac{dm} command, $\mathcal{E}_{s}$ the stellar speckles in the coronagraphic focal plane and $\mathcal{E}_{\mathrm{DM}}$ the speckles created by the \ac{dm}.
%
Effectively, \ac{efc} finds the command that injects speckles with the exact same amplitude but opposite phase in the focal plane.
%
\ac{efc} is currently the most used and best optimized algorithm on testbeds and instruments \citep{Mennesson24}.

@@

Estimating the stellar halo with images at nearby wavelengths was generalised with the use of integral field spectrographs, where many science camera \acp{psf} are sampled at different wavelengths simultaneously to form $(x,y,\lambda)$ data cubes.
%
Resampling the image slices into the same \ld{} spatial scale radially smears out any exoplanet signal, so subtracting off a median of these images removes the stellar halo but keeps most of the planet flux intact, making it visible when the median subtracted cube is resampled into the sky coordinates and combined to produce the \ac{psf} subtracted image, generalised as Spectral Differential Imaging \cite[SDI; ][]{Sparks02} and demonstrated on-sky with SINFONI \citep{Thatte07}.
%
For higher spectral resolutions, the spectrum of the exoplanet begins to resolve the individual rotational-vibrational transitions, enabling High Spectral Contrast Imaging \citep[including the detection of HD~209458b ][]{Snellen10} and then generalising into the principle of molecule mapping in directly imaged exoplanets such as Beta~Pictoris~b \citep{Hoeijmakers18}.

Stochastic Speckle Discriminaton \citep[SSD; ][]{Gladysz09} is possible using short exposure images with the Airy core unsaturated.
%
Photon counting devices enable this detection method to work - this was demonstrated using an MKID detector and has led to the discovery of a substellar companion using this technique \citep{Steiger21}.
%
Each diversity improves sensitivity from a factor of a few to ten or more.
%
Combining different diversities together results in an even greater cumulative effect.

@@

To achieve the scientific results presented in this article we made use of the \emph{Python} programming language\footnote{Python Software Foundation, \url{https://www.python.org/}}, especially the \emph{SciPy} \citep{virtanen2020}, \emph{NumPy} \citep{numpy}, \emph{Matplotlib} \citep{Matplotlib}, \emph{emcee} \citep{foreman-mackey2013}, and \emph{astropy} \citep{astropy_1,astropy_2} packages.
%
The \ac{hci} simulations were calculated with \emph{HCIpy} \citep{Por18}.
%
This Article is reproducible using the \emph{showyourwork!} workflow management tool \citep{Luger2021}.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
M.\ A.\ K.\ acknowledges useful conversations with several people (most notably
Phil Hinz, Eric Mamajek and Andrew Skemer) at the Humble Sea Brewing Company.
